Kaggle-in-class Data Challenges can Boost Student Learning

### 2018-03-15 paper-kaggle.Rmd
added monash

# Participants

@@

@@

## Test scores

@@

### Examining individual questions

@@

>>>>

# Experimental setup

## Data collection

Explain experimental design: two compeitions, two locations, two courses, one with students randomised into two groups, the other with control group of students and regression challenge, and exam questions. (Not sure how to incorporate ETC3250 students at the moment.)

## Participants

@@

## Competitions

@@

## Performance

@@

**Examining individual questions**

@@

### Monash students

Figure \ref{fig:ETC5242} shows the results for students in the Statistical Thinking course at Monash University. Only the post-graduate students participated in the regression competition, as their additional assessment requirement. Scores for the question on regression in the final exam were compared with the total exam score (PTE defined earlier). The boxplots suggest that the students who participated in the challenge performed realtively better on the regression question than expected given their total exam performance: the median is higher and there is less variability.

```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in the Statistical Thinking course at Monash."}
library(tidyverse)

scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
#summary(scores_5242$`7b (8)`)
#summary(scores_2420$`7b (8)`)

scores_5242$`Exam Tot` <- apply(scores_5242[,4:27],1,sum, na.rm=T)
scores_2420$`Exam Tot` <- apply(scores_2420[,4:27],1,sum, na.rm=T)

scores_5242 <- scores_5242 %>% mutate(perf = `7b (8)`/`Exam Tot`)
scores_2420 <- scores_2420 %>% mutate(perf = `7b (8)`/`Exam Tot`)
scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
  filter(!is.na(perf))
scores_2420 <- scores_2420 %>% mutate(class="No") %>%
  filter(!is.na(perf))

#summary(scores_5242$perf)
#summary(scores_2420$perf)
scores <- bind_rows(scores_5242, scores_2420)
ggplot(scores, aes(x=class, y=perf)) + 
  geom_boxplot() + 
  xlab("Participated in regression competiton") +
  ylab("Score relative to total score")
```

```{r permtest}
pdif <- NULL
for (i in 1:1000) {
  x <- scores %>% select(class, perf)
  x <- x %>% mutate(class = sample(class))
  pdif <- c(pdif,
            mean(x$perf[x$class=="Yes"]-
                   mean(x$perf[x$class=="No"])))
}
dif <- mean(scores$perf[scores$class=="Yes"]-
       mean(scores$perf[scores$class=="No"]))
```
```{r}
tt <- t.test(scores$perf[scores$class=="Yes"], scores$perf[scores$class=="No"], alternative="greater")
```

On average the students who participated in the kaggle challenge scored `r dif` higher than those that didn't, `r mean(scores$perf[scores$class=="Yes"])` in comaprison to `r mean(scores$perf[scores$class=="No"])`. Using a permutation t-test, this corresponds to a significant difference in means, with $p$-value of `r length(pdif[pdif >= dif])/1000`. A conventional $t$-test, yields similar results with a $p$-value of `r tt$p.value`.
